The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
unitless

## Each metric's interpretation
* Multidegree: sum of degree across layers. High multidegree = connected to many
individuals across layers. Low multidegree = not connected to many individuals
across layers.

* Degree deviation: deviation of degree across layers. High degree deviation =
large difference between degree for an individual across layers. Low degree
deviation = individuals are similarly connected across layers.

* Graph strength: weighted version of degree. High graph strength = highly
connected. Not summed in this case across layers.

@@

* Neighbourhood: number of unique individuals across all layers. High
neighbourhood = a high number of unique individuals connected to an actor.

@@

(ref:socres) Varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest. This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 **[JWT: Does this have units??]** at approximately a 50m **??** social threshold before decreasing between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections. **[JWT: I'm not sure sparse is the best word, they don't have strong connections, which is related to the number of associations, but it also has to do with the SRI. I would talk about it more about strong/weak connections. Networks can be sparse (few connections), but still have high strength if the ties have higher values]**

>>>>

## Each metric's interpretation
**[JWT: Do we need to define degree first since degree is mentioned in so many of our definitions?]**
* Degree: the number of direct connections an individual has to other individuals in the network. High degree = connected to many indviduals in a single layer. Low degree = not connected to many individuals in a single layer.

* Multidegree: sum of degree across layers. High multidegree = connected to many
individuals across layers. Low multidegree = not connected to many individuals
across layers.

* Degree deviation: standard **[??]** deviation of degree across layers. High degree deviation =
large difference between degree for an individual across layers. Low degree
deviation = individuals are similarly connected across layers.

* Graph strength: the sum of all the edge weights directly connected to an actor, sometimes called weigthed degree. High graph strength = highly social, connected to many individuals and/or having stronger, high-valued connections between individuals. Low graph strength = not very social, connected to few individuals and/or having weak, low-valued connections between individuals. Not summed in this case across layers.

@@

* Neighbourhood: number of unique individuals across all layers. High
neighbourhood = a high number of unique individuals connected to an actor. Low
neighbourhood = a low number of unique individuals connected to an actor.

@@

(ref:socres) Varying scale in social threshold. For each social threshold (5m, 50m, 100m, 150m, 200m, 250m, 300m, 350m, 400m, 450m, 500m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter) and four network metrics calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an overall increase in similarity for open layers and decrease in similarity for lichen layers.**[JWT: what about forest. This made me realize that the legend isn't wide enougth to really tell the difference between lty, forest and open look the same in the legend]** B) Mean connective redundancy across individuals increased rapidly between 5m and 50m reaching a plateau  of about 0.65 at approximately a 50m **??** social threshold before decreasing between 400m and 500m. C) Mean layer relevance was relatively stable across social thresholds for each season and landcover layer. D) Mean graph strength across individuals showed an increase for winter network layers at 50m through 500m while summer network layers had consistently weak connections. **[JWT: I'm not sure sparse is the best word, they don't have strong connections, which is related to the number of associations, but it also has to do with the SRI. I would talk about it more about strong/weak connections. Networks can be sparse (few connections), but still have high strength if the ties have higher values]**
